\documentclass[11pt]{article}
\usepackage{amsmath, amssymb, amsfonts}
\usepackage{quantum} % Custom macros for phase, entanglement, etc.
\usepackage{tikz}
\usetikzlibrary{decorations.pathmorphing, arrows.meta}
\usepackage{cleveref}
\usepackage{geometry}
\usepackage{hyperref}
\geometry{margin=1in}

\title{Appendix A: Chronometric Valuation Model (CVM)}
\author{Umair Abbas \\ \href{https://orcid.org/0009-0008-3968-2252}{ORCID: 0009-0008-3968-2252}}
\date{\today}

\begin{document}
\maketitle

\section{Foundations: Temporal Phase-Space}
Let $\mathcal{T}$ denote the physical time manifold, and let $\mathcal{A} = \{a_0, a_1, \dots\}$
be a set of \textbf{chronal anchors}—events with invariant temporal significance (e.g.,
cosmological singularities, systemic financial inflection points). For any anchor $a_k$, define its
proper chronal coordinate:
\[
\tau_k := \int_{t_{\text{ref}}}^{t_k} \frac{dt}{\sqrt{1 - \beta(t)^2}} \quad \text{(relativistic proper time
analog)}
\]
where $\beta(t)$ encodes economic inertia (e.g., policy response lag, market memory decay).
The \textbf{phase mapping} for harmonic period $P_k$ is:
\begin{equation}
\theta_k(t) = 2\pi \cdot \left\{ \frac{t - \tau_k}{P_k} \right\} \in [0, 2\pi)
\end{equation}
where $\{\cdot\}$ denotes fractional part (mod 1), ensuring periodicity.

\section{Multi-Harmonic Temporal Lattice}
Define a \textit{temporal lattice} $\Lambda \subset \mathbb{R}^n$ as:
\[
\Lambda = \bigoplus_{k=1}^{N} \mathbb{Z} \cdot \mathbf{e}_k, \quad \mathbf{e}_k = \left(
\cos\theta_k(t), \sin\theta_k(t) \right)
\]
Each event $E_i$ at time $t_i$ maps to a point:
\[
\vec{\Theta}(t_i) = \left( \theta_1(t_i), \theta_2(t_i), \dots, \theta_N(t_i) \right) \in \mathbb{T}^N
\]
the $N$-torus of harmonic phases.
Let $\mathcal{H} = \{P_3, P_6, P_9, P_{12}\}$ be the canonical harmonic set (motivated by
empirical cycle clustering in macroeconomics and solar-terrestrial systems).

\section{Chronometric Valuation Operator}
Let $CF_i$ be the cash flow at $t_i$. Define the \textbf{valuation kernel}:
\begin{equation}
\mathcal{K}_k(t_i) = \exp\left( i \, \omega_k \theta_k(t_i) \right) \cdot \rho_k(t_i)
\end{equation}
where:
\begin{itemize}
\item $\omega_k = 2\pi / P_k$ is the angular frequency,
\item $\rho_k(t_i) = \exp\left(-\gamma_k \cdot d_{\text{geo}}(t_i, a_k)\right)$ is a geodesic
damping factor ($d_{\text{geo}}$ = temporal distance along causal path),
\item $\gamma_k > 0$ controls harmonic relevance (learned via citation-network attention
over SideChannel/HardwareCrypto clusters).
\end{itemize}
Then the \textbf{Chronogeometric Value} of a stream $\{CF_i\}_{i=1}^M$ is:
\begin{equation}
\boxed{
V_{\text{CVM}} = \Re\left[ \sum_{i=1}^M CF_i \cdot \sum_{k=1}^{N} w_k \, \mathcal{K}_k(t_i)
\right]
}
\end{equation}
with weights $w_k$ normalized: $\sum_k w_k = 1$, derived from entropy minimization over
historical resonance events.

\section{Temporal Resonance Metric}
Two events $E_i, E_j$ exhibit \textbf{temporal resonance} iff:
\begin{equation}
\Delta\theta_{ij}^{(k)} = \left| \theta_k(t_i) - \theta_k(t_j) \right| < \epsilon_k \quad \forall k \in
\mathcal{S}
\end{equation}
for a subset $\mathcal{S} \subseteq \{1,\dots,N\}$ and tolerance $\epsilon_k \ll 2\pi$. Define the
resonance strength:
\begin{equation}
\mathcal{R}(E_i, E_j) = \prod_{k \in \mathcal{S}} \cos^2\left( \frac{\Delta\theta_{ij}^{(k)}}{2} \right)
\end{equation}
This is structurally analogous to quantum fidelity between coherent states.

\section{Connection to Quantum Block Torch (QBT)}
Under QBT, the valuation $V_{\text{CVM}}$ can be certified via a zero-knowledge proof:
\[
\pi = \text{ZKProof}\big( \{CF_i\}, \{\theta_k(t_i)\}, \mathcal{R} \big)
\]
using lattice-based commitments (e.g., Dilithium-style) and FHE-evaluated phase
sums—ensuring privacy-preserving auditability.

\end{document}
